---
title: "Advertisement Survey Dynamic Report"
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  error = FALSE
)

library(tidyverse)

if (!exists("latest_data")) {
  logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRXth27lgkwB03wZMIcgRUmDbYwLB9-rWO_6jS8kEG6tStVfCspbiK37AgQczb6hC1Nh7KmmqNORYGO/pub?output=csv")

  old_names <- names(logged_data)

  latest_data <- logged_data %>%
    rename(
      timestamp = all_of(old_names[1]),
      ad_type = all_of(old_names[2]),
      ad_length = all_of(old_names[3]),
      click_likelihood = all_of(old_names[4])
    ) %>%
    mutate(ad_length = as.numeric(ad_length))
}
```

## Tracking advertisement type and click likelihood

This dynamic report summarises responses from an advertisement survey dataset.  
It focuses on the type of advertisement shown, the length of the advertisement, and how likely respondents are to click on it.

```{r summary-data}
summary_data <- latest_data %>%
  summarise(
    total_responses = n(),
    min_length = min(ad_length, na.rm = TRUE),
    mean_length = mean(ad_length, na.rm = TRUE)
  )
```

There were `r summary_data$total_responses` responses in this survey.

The shortest advertisement lasted `r summary_data$min_length` seconds.

The average advertisement length was `r round(summary_data$mean_length, 2)` seconds.

## Advertisement type responses

This bar chart shows the number of responses for each advertisement type.

```{r ad-type-plot}
latest_data %>%
  ggplot(aes(x = ad_type)) +
  geom_bar() +
  labs(
    title = "Type of advertisement",
    x = "Advertisement type",
    y = "Count"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Click likelihood responses

This bar chart shows how likely respondents are to click on the advertisement.

```{r click-plot}
latest_data %>%
  ggplot(aes(x = click_likelihood)) +
  geom_bar() +
  labs(
    title = "Likelihood of clicking the advertisement",
    x = "Click likelihood",
    y = "Count"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


Summary

This dataset contains responses from 45 participants in an advertisement survey. 
It includes information about the type of advertisement, the advertisement length in seconds, and respondents’ likelihood of clicking on the advertisement. 
The shortest advertisement length in the dataset was `r summary_data$min_length` seconds, and the average advertisement length was `r round(summary_data$mean_length, 2)` seconds. 
Overall, the data helps show both the distribution of advertisement categories and how participants responded to them.
